---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.align = "center"
)

```


```{r data, echo=FALSE, message=FALSE, warning=FALSE}

# Create a 3x2 grid
library(ggplot2)
library(ggfitz)
library(emwthemes)
library(scales)

```



# ggfitz

<!-- badges: start -->

[![R-CMD-check](https://github.com/emmarshall/ggfitz/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/emmarshall/ggfitz/actions/workflows/R-CMD-check.yaml)

<!-- badges: end -->

The `ggfitz` package is designed for personal use and teaching the power of Fitz to students of data science. It provides an easy to use geom for adding Fitz to ggplot2 objects.  

## Installation
```r
# install.packages("devtools")
devtools::install_github("emmarshall/ggfitz")
```

## Examples

```{r default, echo=FALSE, messages=FALSE, warning=FALSE, eval=TRUE}



# Simple example
ggplot(data.frame(x=1, y=1, image="fitz"), aes(x, y)) +
  geom_fitz(aes(fitz = image), size = 3) +
    theme_em() +
               labs(title = "Fitz (default)",
       subtitle = "Isn't he cute?") +
        theme(
          axis.line = element_blank(),
          axis.text = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank())

```


```{r options, echo=FALSE, messages=FALSE, warning=FALSE, eval=TRUE}

# Create a data frame with all six Fitz images
df <- data.frame(
  x = c(1, 2, 3, 1, 2, 3),
  y = c(2, 2, 2, 1, 1, 1),
  image = c("smart", "student", "sleep", "shade", "cool", "captain")
)

# Custom function to plot multiple Fitz images
plot_multi_fitz <- function(df) {
  p <- ggplot(df, aes(x, y))
  for(i in 1:nrow(df)) {
    p <- p + geom_fitz(data = df[i,], aes(fitz = image), size = 2.5) +
       geom_label(aes(x = x, y = y - 0.25, label = image), 
                 data = df[i,], size = 4, fontface = "bold", fill = "white")
  }
  return(p)
}
 
# Create and display the plot
plot_multi_fitz(df) +
  theme_em() +
  scale_x_continuous(limits = c(0.5, 3.5)) +
  scale_y_continuous(limits = c(0.5, 2.5)) +
  labs(title = "Other `Fitz_Geoms`",
       subtitle = "Includes: smart, student, sleep, shade, cool, captain") +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank(),
        panel.grid = element_blank())


```


## Fitz `(default)`
```{r fitz, messages=FALSE, warning=FALSE, eval=TRUE}
ggplot(mtcars) +
  geom_fitz(aes(mpg, wt), fitz = "fitz") + theme_em()
```


## Fitz `smart`

```{r smart, echo=FALSE, messages=FALSE, warning=FALSE, eval=TRUE}
ggplot(mtcars) +
  geom_fitz(aes(mpg, wt), fitz = "smart") + theme_em()
```




## Fitz `student`

```{r student, echo=FALSE, messages=FALSE, warning=FALSE, eval=TRUE}
ggplot(mtcars) +
  geom_fitz(aes(mpg, wt), fitz = "student") + theme_em()
```


## Fitz `sleep`

```{r sleep, echo=FALSE, messages=FALSE, warning=FALSE, eval=TRUE}
ggplot(mtcars) +
  geom_fitz(aes(mpg, wt), fitz = "sleep")
```



## Fitz `shade`

```{r shade, echo=FALSE, messages=FALSE, warning=FALSE, eval=TRUE}
ggplot(mtcars) +
  geom_fitz(aes(mpg, wt), fitz = "shade") + theme_em()
```



## Fitz `cool`

```{r cool, echo=FALSE, messages=FALSE, warning=FALSE, eval=TRUE}
ggplot(mtcars) +
  geom_fitz(aes(mpg, wt), fitz = "cool") + theme_em()
```

## Fitz `captain`

```{r captain, echo=FALSE, messages=FALSE, warning=FALSE, eval=TRUE}
ggplot(mtcars) +
  geom_fitz(aes(mpg, wt), fitz = "captain") + theme_em()
```


## Acknowledgements

This package is inspired by the [`ggbernie`](https://github.com/R-CoderDotCom/ggbernie) and [`ggcats`](https://github.com/R-CoderDotCom/ggcats) packages from the memeverse. My primary contribution was the Fitz. 



